---
title: "R for Data Science"
author: "David Bessenyei"
date: '2022-03-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

## 1.4 Prerequisites

```{r}
install.packages(c("tidyverse","nycflights13", "gapminder", "Lahman"))
```

```{r}
library(tidyverse)
library(nycflights13)
library(gapminder)
library(Lahman)
```


# Part I. Explore

## 2 Introduction

## 3 Data visualisation

> R has several systems for making graphs, but ggplot2 is one of the most elegant and most versatile.

```{r}
mpg
```

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy))
```

#### 3.2.3 A graphing template

```{r eval=FALSE, include=TRUE}
ggplot(data = <DATA>) + 
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```


#### 3.2.4 Exercises

- Run ggplot(data = mpg). What do you see?
- How many rows are in mpg? How many columns?
- What does the drv variable describe? Read the help for ?mpg to find - out.
- Make a scatterplot of hwy vs cyl.
- What happens if you make a scatterplot of class vs drv? Why is the plot not useful?

##### 3.2.4.1 Run ggplot(data = mpg). What do you see?

```{r}
ggplot(data = mpg)
```
It's just the blank canvas. No data is shown, because we have not mapped it to any geom.

##### 3.2.4.2 How many rows are in mpg? How many columns?

234 rows, 11 columns. It was displayed when I have printed the dataframe previously.

```{r}
number_of_columns_mpg <- length(mpg)
number_of_columns_mpg
```

```{r}
number_of_records_mpg <- mpg |> 
  summarise(number_of_records = n())
number_of_records_mpg
```


```{r}
number_of_records_mpg <- mpg %>% 
  summarise(number_of_records = n()) %>% 
  .[[1]]
number_of_records_mpg
```


# Part II. Wrangle

# Part III. Program

# Part IV. Model

# Part V. Communicate





